---
title: "Untitled"
author: "Jian(Frank)"
date: "27/01/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(scipen=999)
source("scripts/pkgs.R")
source("scripts/functions.R")
```

## Import data 

```{r read data, echo = TRUE}
data <- fread("Data/cleaned.csv")
# clean data
# data[, Item_Fat_Content:=ifelse(Item_Fat_Content %in% c("low fat", "LF", "Low Fat"),
#                                 "Low Fat", 
#                                 ifelse(Item_Fat_Content == "reg", "Regular", Item_Fat_Content))]

```

# Goals:
-	Build a model to predict the number of sales (Item_Outlet_Sales) using the available features.
-	Gain insights about the number of sales.

-	Pretend you are presenting the results to an executive level manager of one of our clients.



item_outlet_sales ~ f(x)

```{r}
cate_cols <- sapply(data, function(x) {
  x <- ifelse(is.character(x), 1, 0)
  x
  })
colnames(data)
catecols_pos <- names(which(cate_cols == 1))
cate_data <- data[,..catecols_pos]
cate_data

apply(cate_data[, Item_Identifier := NULL], 2, unique)
```
Outlet_size have null values. 

## The top 10 popular Product
```{r}
product_type <- data[, sum(Item_Outlet_Sales), 
                     by = .(Item_Fat_Content, Item_Identifier)
                     ][1:10]

product_type %>% 
  ggplot(aes(fct_reorder(Item_Identifier, V1),V1, fill = Item_Fat_Content))+
  geom_col()+
  coord_flip() +
  labs(title = "Top 10 Best Selling Products", 
       y = "",x = "") +
  theme_minimal()+
  theme( title = element_text(size = 18, face = "bold"),
         axis.text = element_text(size = 13),
         axis.title = element_text(size = 9, vjust =  "rt"),
         plot.margin = margin(30, 30, 30, 30), 
         panel.spacing =  grid::unit(2, "lines"),
         legend.position = c(.85,.2),
         legend.background = element_rect(fill = "white"))+
  scale_y_comma(limits=c(0,50000)) +
  scale_fill_manual(name = "Fat Content", values = corporate_colors[1:2])+
  geom_text(aes(label=scales::comma(V1)), hjust=0, nudge_y=500) 

ggsave("Reports/top10products.png", width = 8, height = 6, dpi = 300)
```

low fat products are popular. 
In the top 30 selling products, top 3 are low fat products. 
16 out of 30 are still regular products (2 products are fruit and vegetables).
Provide alternative low fat products for the rest of 14 regular products may boost sales?

## The most popular Product Type


```{r, fig.width=9}
product_type <- data[, sum(Item_Outlet_Sales), by = .(Item_Type, Item_Fat_Content)
                     ][, total := sum(V1), by = .(Item_Type)
                       ][, pct := round(V1/total, digits = 2)]
sales_rank <- data[, sum(Item_Outlet_Sales), by =.(Item_Type)
                   ][order(V1, decreasing = TRUE)
                     ][, price_label := as.character(paste0("~", round(ceiling(V1)/1000), "K"))]
product_type <- product_type[sales_rank, on = "Item_Type"]

product_type$Item_Type <- factor(product_type$Item_Type, levels = rev(sales_rank$Item_Type))
product_type %>% 
  ggplot(aes(Item_Type,V1, fill = Item_Fat_Content))+
  geom_bar(stat = "identity", position = "stack")+
  coord_flip() +
  labs(title = "Overall Best Selling Product Types", 
       y = "",x = "") +
  theme_minimal()+
  theme( title = element_text(size = 18, face = "bold"),
         axis.text = element_text(size = 16),
         axis.title = element_text(size = 9, vjust =  "rt"),
         plot.margin = margin(30, 30, 30, 30), 
         panel.spacing =  grid::unit(2, "lines"),
         legend.position = c(.85,.2),
         legend.background = element_rect(fill = "white"))+
  scale_y_comma(limits=c(0,3500000)) +
  scale_fill_manual(name = "Fat Content", 
                    values =  corporate_colors[1:2]) 
  # geom_text(aes(y = i.V1 + 350000 , label= price_label), size = 5)
ggsave("Reports/topproducttypes.png", width = 9, height = 6, dpi = 300)


```



## The most popular store 

```{r, fig.width=9}
popular_store <- data[, sum(Item_Outlet_Sales), by = .(Outlet_Type, Outlet_Identifier)]
popular_store  %>% 
  ggplot(aes(fct_reorder(Outlet_Identifier, V1),V1, fill = Outlet_Type))+
  geom_col()+
  coord_flip() +
  labs(title = "Total sales in each Outlet", 
       y = "",x = "") +
  min_theme()+
  scale_y_comma(limits=c(0,4000000)) +
  theme(legend.position = c(.85,.25),
         legend.background = element_rect(fill = "white")) +
  scale_fill_manual(name = "Outlet Type", values = corporate_colors,
                    guide = guide_legend(reverse = TRUE)) +
  geom_text(aes(label=scales::comma(V1)), hjust=0, nudge_y=5000) 

ggsave("Reports/storesales.png", width = 9, height = 6, dpi = 300)
```


## pattern between item mpr and log10 sales


```{r}
data %>% 
  ggplot(aes(Item_MRP, log10(Item_Outlet_Sales),
             color = Outlet_Type)) +
  geom_jitter(alpha = 0.3) +
  geom_boxplot(alpha = 0.5) +
  geom_smooth(method = "loess", se = FALSE, size = 3) +
  scale_color_manual(name = "Outlet Type",values = corporate_colors)+
  min_theme()+
  theme( title = element_text(size = 18, face = "bold"),
         axis.text = element_text(size = 13),
         axis.title = element_text(size = 16, vjust =  "rt"),
         plot.margin = margin(30, 30, 30, 30), 
         panel.spacing =  grid::unit(2, "lines"))+
  labs(x = "Maximum Retail Price", 
       y = "Item Outlet Sales (log10)")

ggsave("Reports/mrpvsoutletsales.png", width = 9, height = 6, dpi = 300)


```


```{r}
cat_cols <- which(sapply(data, is.character) == 1)

unique(data[, ..cat_cols])


data %>% 
  ggplot(aes(Item_MRP, Item_Outlet_Sales, color = Outlet_Type)) +
  geom_boxplot(alpha = 0.8) +
  # geom_smooth(method = "loess") +
  scale_color_manual(values = corporate_colors) +
  min_theme()
  
```
```{r}
lmfit <- lm(Item_)
```

**Type1 and 2 can be combined into one class. **



## outlet type sales generation 

```{r}
popular_store <- data[, sum(Item_Outlet_Sales), by = .(Outlet_Type)
                      ][, pct := paste0(round(V1/sum(V1), digits = 2) * 100, "%")]
popular_store  %>% 
  ggplot(aes(fct_reorder(Outlet_Type, V1),V1))+
  geom_col(fill = corporate_colors[2])+
  coord_flip() +
  labs(title = "The Most Popular Outlet Type", 
       y = "",x = "") +
  min_theme()+
  scale_y_comma(limits=c(0,max(popular_store$V1) * 1.2)) +
  scale_fill_manual(name = "Outlet Type", values = corporate_colors,
                    guide = guide_legend(reverse = TRUE)) +
  geom_text(aes(label=pct), hjust=0, nudge_y=5000) 
ggsave("Reports/typesalespct.png", dpi = 300)

(popular_store$V1[1] + popular_store$V1[2]) * 0.01/sum(popular_store$V1)
(popular_store$V1[4] * 0.01)
```


```{r}
data <- fread("Data/lmtestrs.csv")
data %>% 
  melt.data.table(variable.factor = FALSE) %>% 
  ggplot(aes(value, fill = variable)) +
  geom_histogram( position = position_dodge(),binwidth = 300, bins = 30) +
  min_theme() +
  theme(legend.position = c(.9,.85),
        legend.background = element_rect(colour = "black"),
        legend.box.background = element_rect(colour = "white"),
        legend.title = element_blank(),
        title = element_text(size = 18, face = "bold"),
         axis.text = element_text(size = 13),
         axis.title = element_text(size = 16, vjust =  "rt"),
         plot.margin = margin(30, 30, 30, 30), 
         panel.spacing =  grid::unit(2, "lines"))+
  labs(x = "Item Outlet Sales", 
       y = "Distribution",
       title = "True Sales vs Predicted Sales Distribution Comparision",
       subtitle = "Linear Regression Model")+
      scale_fill_manual(name = '', values = corporate_colors[c(2, 4)], labels = c("True Sales", "Predict Sales") )


ggsave("Reports/true_pred.png", width = 9, height = 6, dpi = 300)


```


```{r}
baselines <- fread("Data/baselines.csv")
rank =baselines[, mean(r2), by = .(names)
          ][order(V1, decreasing = T)][, rank := 1:.N]

baselines$names <- factor(baselines$names, levels = rank$names)
baselines %>% 
  ggplot(aes(names, r2)) +
  geom_boxplot() +
  min_theme() +
  theme(title = element_text(size = 18, face = "bold"),
        axis.text = element_text(size = 13), 
        plot.caption = element_text(size = 12),
        axis.title = element_text(size = 16, vjust =  "rt"),
        plot.margin = margin(30, 30, 30, 30), 
        panel.spacing =  grid::unit(2, "lines"))+
  labs(x = "Models", 
       y = "Coefficient of determination",
       title = "Six Models Performance Evaluation",
       caption = "Boxplot resulted from 10 fold cross validation ")



ggsave("Reports/modelseletion.png", width = 9, height = 6, dpi = 300)

  
```
## visual glm features

```{r}
glm <- fread("Data/glm.csv")
glm <- glm %>% 
  melt.data.table(variable.factor = FALSE)
glm[value > 0.01][order(value, decreasing = T)][1:5] %>% 
  ggplot(aes(fct_reorder(variable, value),value)) +
  geom_col(fill = corporate_colors) +
  coord_flip() +
  min_theme()+
  labs(x = "Features", 
       y = "Coefficient",
       title = "Top Five Predictors",
       subtitle = "Generalised Linear Model")+
      scale_fill_manual(name = '', values = corporate_colors[c(2, 4)], labels = c("True Sales", "Predict Sales") )


ggsave("Reports/glmfeatureranks.png", width = 9, height = 6, dpi = 300)
```

## visual rf grid search 

```{r}
top10_rf_para <- fread("Data/rf_gridsearch.csv")
cols <- colnames(top10_rf_para)
top10_rf_para[, para_combi := paste(bootstrap,max_depth,max_features,n_estimators, sep = "\n")]
top10_rf_para %>% 
  ggplot(aes(rank_test_score, mean_test_score)) +
  geom_line()
  
```
```{r}
topfeatures <- fread("Data/rf_featureimpt.csv")

topfeatures[value > 0.001] %>% 
  ggplot(aes(forcats::fct_reorder(V1, value),value)) +
  geom_col(fill = corporate_colors[c(5, 5:1)]) +
  coord_flip() +
  min_theme()+
  labs(x = "Features", 
       y = "Importance",
       title = "Top Six Predictors",
       subtitle = "Random Forest")



ggsave("Reports/rffeatureranks.png", width = 9, height = 6, dpi = 300)

```

## Why store 10 and 19 are so small on sales? 
```{r}
data[Outlet_Type %like% 3 ]
data[Outlet_Identifier %in% c("OUT010", "OUT019")]$Outlet_Type %>% unique()

unique(data[,.(Outlet_Identifier, Outlet_Establishment_Year, Outlet_Type, 
               Outlet_Location_Type = as.character(Outlet_Location_Type))]) %>% 
  ggplot(aes(forcats::fct_reorder(Outlet_Identifier, Outlet_Establishment_Year, .desc = TRUE),
             Outlet_Establishment_Year, color = Outlet_Type, shape = Outlet_Location_Type)) +
  geom_point(size = 3)+
  coord_flip() +
  scale_y_continuous(position = "right") +
  min_theme() +
  labs(x = "Outlet Identifier", 
       y = "Establishment Year") +
  scale_color_manual(name = "Outlet Type", values = corporate_colors,
                    guide = guide_legend(reverse = TRUE))
  
```
OUT010 and 019 are Grocery Stores 

## Does Location affect sales?
```{r}

popular_store <- data[, sum(Item_Outlet_Sales), by = .(Outlet_Location_Type)]
popular_store[, Outlet_Location_Type := as.character(Outlet_Location_Type)]  %>% 
  ggplot(aes(fct_reorder(Outlet_Location_Type, V1),V1, fill = Outlet_Location_Type))+
  geom_col()+
  coord_flip() +
  labs(title = "The Most Popular Store", 
       y = "",x = "") +
  min_theme()+
  scale_y_comma(limits=c(0,8000000)) +
  scale_fill_manual(name = "Outlet  Location Type", values = corporate_colors,
                    guide = guide_legend(reverse = TRUE)) +
  geom_text(aes(label=scales::comma(V1)), hjust=0, nudge_y=5000) 


data[, .(Item_Outlet_Sales,Outlet_Location_Type)] %>% 
  ggplot(aes(Outlet_Location_Type, Item_Outlet_Sales, group = Outlet_Location_Type))+
    geom_jitter(alpha = .3)+
  geom_boxplot()


```
The **long tail* created the skewness, what are these? 

```{r, fig.height= 15, fig.width= 8}
outliner_items <- data

outliner_items %>% 
  ggplot(aes( Item_MRP, Item_Outlet_Sales, color = Item_Visibility)) +
  geom_jitter() +
  facet_grid(  Item_Fat_Content + Item_Type ~ Outlet_Size + Outlet_Type + Outlet_Identifier)
```
## what if filter out gocery stores?
```{r, fig.height=7}
outliner_items <- data[!Outlet_Type %like% "Gro"]

outliner_items %>% 
  ggplot(aes( Item_MRP, Item_Outlet_Sales, color = Outlet_Type)) +
  geom_jitter()


outliner_items %>% 
  ggplot(aes(Item_MRP)) +
  geom_histogram(binwidth = 2)

```

## Item visibility
```{r}
range(data$Item_Visibility)
data %>% 
  ggplot(aes(Item_Visibility)) +
  geom_histogram(binwidth = 0.001)
```

## Fat content matters?

```{r, fig.width=9}
product_type <- data[, sum(Item_Outlet_Sales), by = .(Item_Fat_Content)]
product_type %>% 
  ggplot(aes(Item_Fat_Content,V1))+
  geom_col(fill = corporate_colors[2])+
  # coord_flip() +
  labs(title = "Product Fat Content in relation to total sells", 
       y = "",x = "") +
  theme_minimal()+
  theme( title = element_text(size = 18, face = "bold"),
         axis.text = element_text(size = 13),
         axis.title = element_text(size = 9, vjust =  "rt"),
         plot.margin = margin(30, 30, 30, 30), 
         panel.spacing =  grid::unit(2, "lines"))+
  scale_y_comma(limits=c(0,15500000)) +
  geom_text(aes(label=scales::comma(V1)), size= 8, nudge_y=1500000) 
```


Two large categories of product types are not consumable but in low fat

```{r}
data %>% 
  ggplot(aes(Item_Type, Item_Outlet_Sales, color = Item_Fat_Content)) +
  geom_boxplot()+
  coord_flip()
```



```{r}
data%>% 
  ggplot(aes(log(Item_Outlet_Sales)))+
  geom_histogram()

data[Item_Outlet_Sales > 10000]


for(i in catecols_pos[-1]){
  key <- i
  
  sums <- data[, .(topsales = sum(Item_Outlet_Sales, na.rm = TRUE)), 
               by = key
               ][order(topsales, decreasing = TRUE)] 
  p <- sums %>% 
    ggplot(aes(forcats::fct_reorder(sums[[key]], topsales), topsales)) +
    geom_col() +
    coord_flip()
  print(p)
}
data[Item_Outlet_Sales < 100]
```
 Super market type 1 generate lots of sales 


## Boruta pkg can do feature selection 

```{r}
library(Boruta)

boruta_output <- Boruta(Item_Outlet_Sales ~ ., 
                        data=na.omit(data[, Item_Identifier :=NULL]), doTrace=0)  

names(boruta_output)

boruta_output$finalDecision

boruta_signif <- getSelectedAttributes(boruta_output, withTentative = TRUE)
print(boruta_signif)  
roughFixMod <- TentativeRoughFix(boruta_output)
boruta_signif <- getSelectedAttributes(roughFixMod)
imps <- attStats(roughFixMod)
imps2 = imps[imps$decision != 'Rejected', c('meanImp', 'decision')]
head(imps2[order(-imps2$meanImp), ])  # descending sort
plot(boruta_output, cex.axis=.7, las=2, xlab="", main="Variable Importance")  

decision <- as.character(boruta_output$finalDecision)
names(boruta_output$finalDecision) <- decision 

str(boruta_output)
names(boruta_output$finalDecision)

```

```{r}
data %>% 
  ggplot(aes(Item_MRP, fill = Item_Type))+
  geom_histogram(binwidth = 1)
data %>% 
  ggplot(aes(Item_MRP, fill = Item_Type))+
  geom_histogram(binwidth = 1)

data %>% 
  ggplot(aes(Item_MRP, fill = Outlet_Type))+
  geom_histogram(binwidth = 1)

data %>% 
  ggplot(aes(Item_MRP, fill = Outlet_Size))+
  geom_histogram(binwidth = 1)

data %>% 
  ggplot(aes(Item_MRP, fill = Outlet_Identifier))+
  geom_histogram(binwidth = 1)

```

```{r}
data%>% 
  ggplot(aes(Item_MRP, log10(Item_Outlet_Sales), color = Item_Visibility)) +
  geom_point()+
  geom_smooth(method = "loess", span = 0.5)
data%>% 
  ggplot(aes(Item_MRP, log10(Item_Outlet_Sales), color = Item_Fat_Content)) +
  geom_point()+
  geom_smooth(method = "loess", span = 0.5)
data%>% 
  ggplot(aes(Item_MRP, log10(Item_Outlet_Sales), color = Outlet_Identifier)) +
  geom_point()+
  geom_smooth(method = "loess", span = 0.5)
data%>% 
  ggplot(aes(Item_MRP, log10(Item_Outlet_Sales), color = Outlet_Size)) +
  geom_point()+
  geom_smooth(method = "loess", span = 0.5)

data%>% 
  ggplot(aes(Item_MRP, log10(Item_Outlet_Sales), color = Outlet_Establishment_Year)) +
  geom_point()+
  geom_smooth(method = "loess", span = 0.5)

data%>% 
  ggplot(aes(Item_MRP, log10(Item_Outlet_Sales), color = Item_Type)) +
  geom_point()+
  geom_smooth(method = "loess", span = 0.5)

data%>% 
  ggplot(aes(Item_MRP, log10(Item_Outlet_Sales))) +
  geom_boxplot()
  # geom_smooth(method = "loess", span = 0.5)
```

## select method for feature selection

```{r}
library(caret)
set.seed(42)
rpart <- train(Item_Outlet_Sales ~ log10(Item_MRP) + Outlet_Type, data=na.omit(data), method = "rpart")
rpartimp <- varImp(rpart)

rpartimp
```

```{r}
data %>% 
  ggplot(aes(Outlet_Establishment_Year, log(Item_Outlet_Sales), group = Outlet_Establishment_Year)) +
  geom_boxplot()
data %>% 
  ggplot(aes(Outlet_Establishment_Year, Item_Outlet_Sales, group = Outlet_Establishment_Year)) +
  geom_boxplot()

```
## Regularized Random Forest (RRF) algorithm.
```{r}
set.seed(42)
rrfMod <- train(Item_Outlet_Sales ~ ., data=na.omit(data), method = "rpart")
rrfImp <- varImp(rrfMod, scale=F)
rrfImp

```
## L1

```{r}
library(glmnet)
library(vtreat) # convert categorical variables 
trainData <- read.csv("Data/cleaned.csv")
trainData$Item_Outlet_Sales <- log(trainData$Item_Outlet_Sales)
transform_design <- vtreat::NumericOutcomeTreatment(
    var_list = setdiff(colnames(trainData), c('Item_Outlet_Sales')),  # columns to transform
    outcome_name = 'Item_Outlet_Sales'                        # outcome variable
)

# the unpack notation is a multiassignment operator
# see https://winvector.github.io/wrapr/articles/unpack_multiple_assignment.html
# for more details
library(wrapr)
tf  <- vtreat::fit_prepare(transform_design, trainData)

treatment_plan <- tf$treatments
d_prepared <- tf$cross_frame


# get statistics on the variables
score_frame <- get_score_frame(treatment_plan)
score_frame[score_frame[['recommended']], 'varName', drop = FALSE]


# d_prepared['Item_Outlet_Sales_centered'] <- d_prepared$Item_Outlet_Sales - mean(d_prepared$Item_Outlet_Sales)

WVPlots::ScatterHist(
  d_prepared, 
  xvar = 'Item_Identifier_catN',
  yvar = 'Item_Outlet_Sales',
  smoothmethod = 'identity',
  estimate_sig = TRUE,
  title = 'Relationship between xc_catN and y')

score_frame[score_frame$varName == 'Item_Identifier_catN', ]$rsq

model_vars <- score_frame$varName[score_frame$recommended]
# to use all the variables:
# model_vars <- score_frame$varName

f <- wrapr::mk_formula('Item_Outlet_Sales', model_vars)

model = lm(f, data = d_prepared)

# now predict
d_prepared['prediction'] = predict(
  model,
  newdata = d_prepared)

# look at the fit (on the training data)
WVPlots::ScatterHist(
  d_prepared, 
  xvar = 'prediction',
  yvar = 'Item_Outlet_Sales',
  smoothmethod = 'identity',
  estimate_sig = TRUE,
  title = 'Relationship between prediction and Item_Outlet_Sales')

x <- as.matrix(d_prepared[,-(58:60)]) # all X vars
y <- log(trainData$Item_Outlet_Sales) # Only Class

# Fit the LASSO model (Lasso: Alpha = 1)
set.seed(42)
cv.lasso <- cv.glmnet(x, y, alpha=1, parallel=TRUE, standardize=TRUE, type.measure='auc')

# Results
plot(cv.lasso)
cat('Min Lambda: ', cv.lasso$lambda.min, '\n 1Sd Lambda: ', cv.lasso$lambda.1se)
df_coef <- round(as.matrix(coef(cv.lasso, s=cv.lasso$lambda.min)), 2)

# See all contributing variables
df_coef[df_coef[, 1] != 0, ]
```
## 

```{r}
library(glmnet)
library(vtreat) # convert categorical variables 
trainData <- read.csv("Data/cleaned.csv")

trainData %>% 
  ggplot(aes(Item_Visibility, Item_Outlet_Sales)) +
  geom_jitter()


```